Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-11 methodology.tex
trivial tweak

The parameters for building the dragonfly network studied in our work are chosen based on the model proposed by Kim et al.~\cite{kim-micro}. 
In our dragonfly network, each group consists of $a = 8$ routers connected via all-to-all local channels. For each router, there are $p = 4$ compute nodes attached to it via terminal links. Each router also has $h = 4$ global channels used for intergroup connections. The radix of each router is hence $k = a+h+p-1 = 15$. 
The total number of groups is $g = a*h+1 = 33 $ and the total number of compute nodes is $N = p*a*g = 1056$. 
%\NOTE{What's the resulting router radix? What's the classic $a,h,p$ (or whatever they are :) parameters? done! } 
The dragonfly link bandwidths are 5.25 GiB/s for the local and terminal router-ports and 4.7 GiB/s for the global ports, inspired by the Cray Cascade system~\cite{faanes} 
%\NOTE{What are these bandwidths? done!}. 
In this work, we simulate the network performance and job interference across six different job placement and routing policy combinations, which are summarized in Table~\ref{tab: placement routing configs}.

@@

    \item \textbf{Network Saturation Time:} The saturation time refers to the time period when the buffer of a certain port in the router is full. We analyze the saturation time of ports corresponding to terminal links, local and global channels. The saturated time indicates the congestion level of routers.

>>>>

The parameters for building the dragonfly network studied in our work are chosen based on the model proposed by Kim et al.~\cite{kim-micro}. 
In our dragonfly network, each group consists of $a = 8$ routers connected via all-to-all local channels. For each router, there are $p = 4$ compute nodes attached to it via terminal links. Each router also has $h = 4$ global channels used for intergroup connections. The radix of each router is hence $k = a+h+p-1 = 15$. 
The total number of groups is $g = a*h+1 = 33 $ and the total number of compute nodes is $N = p*a*g = 1056$. 
%\NOTE{What's the resulting router radix? What's the classic $a,h,p$ (or whatever they are :) parameters? done! } 
The dragonfly link bandwidths are 5.25 GiB/s for the local and terminal router-ports and 4.7 GiB/s for the global ports, inspired by the Cray Cascade system~\cite{faanes}.  
%\NOTE{What are these bandwidths? done!}. 
In this work, we simulate the network performance and job interference across six different job placement and routing policy combinations, which are summarized in Table~\ref{tab: placement routing configs}.

@@

    \item \textbf{Network Saturation Time:} The saturation time refers to the time period when the buffer of a certain port in the router is full. We analyze the saturation time of ports corresponding to terminal links, local and global channels. The saturation time indicates the congestion level of routers.
